
\nonstopmode
\documentclass{standalone}

\input{TikZHeader.tex}

\def\pgfsysdriver{pgfsys-tex4ht.def}

\begin{document}
   	\begin{tikzpicture}[vertexStyle, edgeStyle=nolabels, faceStyle]
      	\input{Image_FiveTrianglesInCycle.tex}
   	\end{tikzpicture}
 	</Alt>
 	@BeginExampleSession
 gap> countEdg := CounterOfEdges(fiveStar);
 counter of edges ([ [ 2, 2 ], [ 2, 5 ] ] degrees, and [ 5, 5 ] multiplicities)
 gap> ListCounter(countEdg);
 [ [ [ 2, 2 ], 5 ], [ [ 2, 5 ], 5 ] ]
 	@EndExampleSession
   </Description>
 </ManSection>

 <ManSection Label="CounterOfFaces">
   <Oper Name="CounterOfFaces" Arg="complex"
      Label="for IsTwistedPolygonalComplex"
      Comm="Construct a face counter from a twisted polygonal complex"/>
   <Returns>A Counter-&GAP;-object</Returns>
   <Prop Name="IsCounterOfFaces" Arg="object" Label="for IsObject"
      Comm="Check whether a given object is a face counter"/>
   <Returns><K>true</K> or <K>false</K></Returns>
   <Description>
      The method <K>CounterOfFaces</K> constructs a new face counter from
      a polygonal complex. The method <K>IsCounterOfFaces</K>
      checks if a given &GAP;-object represents such a face counter.
      The face counter saves the information about how many faces have vertices with the same degrees.
 	To get this information there are different possibilities.
 	For example, the method <A>ListCounter</A> (<Ref Subsect="ListCounter"/>) that
 	returns this information as a list of pairs <E>[degreeList, multiplicity]</E>, where
 	<E>multiplicity</E> counts the number of faces whose vertex degrees
 	match <E>degreeList</E>, i.e. for every vertex there is exactly one
 	entry of <E>degreeList</E> such that the vertex is incident to this
 	number of faces.
 	The <E>degreeList</E> is always sorted but may contain duplicates.

	 As an example, consider the five-star from the start of chapter
 	<Ref Chap="Chapter_Properties"/>:
 <Alt Only="TikZ">
   	\begin{tikzpicture}[vertexStyle, edgeStyle=nolabels, faceStyle]
   	   \input{Image_FiveTrianglesInCycle.tex}
   	\end{tikzpicture}
 	</Alt>
 	@ExampleSession
 gap> countFac:=CounterOfFaces(fiveStar);
 counter of faces ([ [ 2, 2, 5 ] ] degrees, and [ 5 ] multiplicities) 
 gap> ListCounter(countFac);
 [ [ [ 2, 2, 5 ], 5 ] ]
 	@EndExampleSession
   </Description>
 </ManSection>

 <ManSection Label="CounterOfButterflies">
   <Oper Name="CounterOfButterflies" Arg="surface"
      Label="for IsSimplicialSurface"
      Comm="Construct a butterfly counter from a simplicial surface"/>
   <Returns>A Counter-&GAP;-object</Returns>
   <Prop Name="IsCounterOfButterflies" Arg="object" Label="for IsObject"
      Comm="Check whether a given object is a butterfly counter"/>
   <Returns><K>true</K> or <K>false</K></Returns>
   <Description>
       The method <K>CounterOfButterflies</K> constructs a new butterfly counter from
       a simplicial surface. The method <K>IsCounterOfButterflies</K>
       checks if a given &GAP;-object represents such a butterfly counter.
 	 The butterfly counter saves the information about how many butterflies have vertices with the same degrees.
       To get this information there are different possibilities.
       For example, the method <A>ListCounter</A> (<Ref Subsect="ListCounter"/>) that
       returns this information as a list of pairs <E>[[degList1,degList2], multiplicity]</E>, where
       <E>multiplicity</E> counts the number of butterflies whose vertex degrees match
       <E>[degList1,degList2]</E>, whereby <E>degList1</E> denotes the
       vertex degree of the vertices that are incident to the edge
       inducing the corresponding butterfly and <E>degList2</E> contains
       the vertex degrees of the two remaining vertices of the butterfly.
 
 	 As an example, consider the double-5-gon:
        <Alt Only="HTML">
 &lt;img src="./images/_Wrapper_Image_Double5gon-1.svg"> &lt;/img>
end{document}